Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-28 Chapter-2/2-LArTPCs.tex
s

The event reconstruction chain uses collection of hits to form more complex objects associated with the particles in the detector. The development of different approaches to accomplish this task is an extremely hot topic in LArTPC event reconstruction which spans from more traditional approaches such as line-clustering  \cite{MicroBooNE} \textcolor{red}{argoneut paper} to the use of machine learning tools \cite{MicroBooNE} \textcolor{red}{KAZU'S paper}. Generally speaking, the scope of hit clustering and event reconstruction to provide shower-like or track like-objects with an associated energy reconstruction. This is because different particles have different topology in the detector -- electrons and photon create electromagnetic showers,  resulting in shower-like topologies, while muons and hadrons  leave track-like signals.  For the scope of these thesis, we will describe only LArIAT's approach to track reconstruction even if we recognize the breath of LArTPC event reconstruction is much wider. We are interested in the reconstruction of pions and kaons in the active volume, whose topology is track-like.\\

>>>>

The event reconstruction chain uses collection of hits to form more complex objects associated with the particles in the detector. The development of different approaches to accomplish this task is an extremely hot topic in LArTPC event reconstruction which spans from more traditional approaches such as line-clustering  \cite{MicroBooNE} \textcolor{red}{argoneut paper} to the use of machine learning tools \cite{1748-0221-12-03-P03011}. Generally speaking, the scope of hit clustering and event reconstruction to provide shower-like or track like-objects with an associated energy reconstruction. This is because different particles have different topology in the detector -- electrons and photon create electromagnetic showers,  resulting in shower-like topologies, while muons and hadrons  leave track-like signals.  For the scope of these thesis, we will describe only LArIAT's approach to track reconstruction even if we recognize the breath of LArTPC event reconstruction is much wider. We are interested in the reconstruction of pions and kaons in the active volume, whose topology is track-like.\\
